---
title: "RMarkdown Plotly"
author: "Alex Cao"
date: "May 3, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r data, message=FALSE}
library(plotly)
data(LifeCycleSavings)
```

## Life Cycle Savings Dataset

- Data on the savings ratio 1960-1970 for 50 countries
- savings ratio = aggregate personal saving divided by disposable income
- plot of **per-capita disposable income** vs. **savings ratio** with *% population under 15* as the color and *% population over 75* as the marker size

***

```{r}
p = plot_ly(LifeCycleSavings, x=~dpi, y=~sr, color=~pop15, size=~pop75, type='scatter', mode='markers', width=800, height=550, text = ~paste(rownames(LifeCycleSavings)))
p
```

## Summary

- USA has the highest per-capita disposable income (4002) but is in the middle of the pack in terms of savings ratio
- Japan has the highest savings ratio (21.1) but is in the middle of the pack in terms of per-capita disposable income
- Zambia saves a lot of money (18.6) and has a lot of income begin with (138)
- Denmark also saves a lot of money (16.9) of its high dispoable income (2497)
- Iceland likes to spend most of its income (1900); savings ratio (1.3)
- Paraguay also spends most of its income but at the other spectrum of income (221); savings ratio (2.0)
- In general, countries with a lot of young people don't have a lot of disposable income and vice versa (makes sense)

